\documentclass{sig-alternate-10pt-CoNEXT}
%\usepackage[small,bf]{caption}
\usepackage{caption}
\usepackage{subfig}
\usepackage{epstopdf}
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{amsmath,amssymb}
\pagenumbering{arabic}
\setlength{\jot}{10pt} 
\renewcommand{\floatpagefraction}{0.8}

\usepackage{url}
%% Define a new 'leo' style for the package.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\normalsize\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}

\hyphenation{Wi-Gem amen-able mar-ginal}
\begin{document}

% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (200X) to be over-ridden - IF NEED BE.
% ACM CoNEXT 2008: the following needs to be over-ridden to include the
% right copyright info
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\pagestyle{empty}
\title{WiGEM : A Learning-Based Approach for Indoor Localization}
%\subtitle{[  Paper Id : 1569469851. Number of Pages : 12 ]}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.
\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Abhishek Goswami, Luis E. Ortiz, Samir R. Das\\
       \affaddr{Computer Science Department, Stony Brook University, Stony Brook, New York 11794, USA}\\
%       \affaddr{Stony Brook University}\\
%       \affaddr{Stony Brook, New York 11794, USA}\\
       \email{agoswami,leortiz,samir@cs.stonybrook.edu}
% 2nd. author
%\alignauthor
%Luis Ortiz
%       \affaddr{Computer Science Department}\\
%       \affaddr{Stony Brook University}\\
%       \email{leortiz@cs.stonybrook.edu}
%% 3rd. author
%\alignauthor 
%Samir R. Das
%       \affaddr{Computer Science}\\
%       \affaddr{Stony Brook University}\\
%       \email{samir@cs.stonybrook.edu}
}

%\date{03 June 2011}

\maketitle
\begin{abstract}
We consider the problem of localizing a wireless client in an
indoor environment based on the signal strength of its transmitted
packets as received on stationary sniffers or access points.
Several state-of-the-art indoor localization techniques have the
drawback that they rely extensively on a labor-intensive`training' phase that does not scale 
well.  Use of unmodeled hardware with heterogeneous
power levels further reduces the accuracy of these
techniques.

We propose a `learning-based' approach, WiGEM, where the received signal
strength is modeled as a Gaussian Mixture Model (GMM). Expectation
Maximization (EM) is used to learn the maximum likelihood estimates of 
the model parameters. 
This approach enables us to localize a transmitting device based on the 
\textit{maximum a posteriori} estimate. The key insight is to use the physics of wireless propagation, 
and exploit the signal strength constraints that exist for different transmit power levels. 
The learning approach not only avoids the 
labor-intensive
training, but also makes the location estimates considerably robust in the face of heterogeneity and 
various time
varying phenomena.  We present evaluations on two different
indoor testbeds with multiple WiFi devices. We demonstrate that WiGEM's
accuracy is at par with or better than state-of-the-art techniques but
without requiring any training.
\end{abstract}

\input{intro}
\input{related}
%\input{wireless}
\input{gmm}
\input{em-algorithm}
\input{exp-methods}
\input{evaluation}
%\newpage
\input{discussion}
\input{conclusion}

%{\color{red}
\section*{ACKNOWLEDGEMENT}
The authors would like to thank Zafar Qazi for help in experiments.
This work was partially supported by NSF grants CNS-0751121, 0831791 and 1117719 and 
an NSF CAREER award IIS-1054541. 
%}

%\newpage
\bibliographystyle{abbrv}
\bibliography{sigproc}  

\end{document}  

